Results

### 2021-08-09 Analysis/03_Summarise_results.Rmd
Comments on last bit of work
(to be removed eventually)

>>>>

# Responses

Carlos:
-TPD richness potential error: 
  * I have double checked the scaling and everything seems OK (but I might be mistaken!) The centreing logic happens here: https://github.com/TGuillerme/eco_metrics_simulations/blob/c2a8deb9d673e0456f315d9a9f43285aafdfea93/Functions/extract.table.R#L59 and the scaling logic happens here: https://github.com/TGuillerme/eco_metrics_simulations/blob/c2a8deb9d673e0456f315d9a9f43285aafdfea93/Functions/extract.table.R#L30 (l.30 to 32)).
  So it might be something with the bandwidth? The whole calculations for the TPD metrics happens here (https://github.com/TGuillerme/eco_metrics_simulations/blob/c2a8deb9d673e0456f315d9a9f43285aafdfea93/Functions/simulation.pipeline.R#L262) with no obvious bandwidth part (at least to my eyes). So maybe it's just using the defaults?

-A minor comment regarding plots:
 - [ ] TODO: reorganise plots labels (follow Stefano's pdf)
 - [ ] TODO: reorganise colours by "Richness / Divergence / Regularity"
 - [ ] TODO: change Convex.hull = Richness; Rao/mpd = Divergence

-Thomas, I would be happy to make the PCAs if you could send me a file with the correlation matrices

 - [ ] TODO: get the scaled results matrices for PCA

Let's talk about the two points on the expectations and the biological realism!

<!-- Carlos comments:

-Sorry to insist on this, but I really disagree with the expectations table as it is, we really would have to discuss what are our expectations (if any!) for any particular mechanism, and what they are based on. This is a big problem for me, since it can give the idea that some particular method (or even all methods) is somehow flawed because it doesnt meet some expectation.

-Biological realism: I think the best at this point would be to use some agent-based model as Pedro suggested. Sure, things interact, but I think we can make a model simple enough and change some parameters on it, so that we can isolate more or less different things. We recently made one for a paper, and I would be happy to adapt the code and run some simulations (after we decide which things we want to play with): https://onlinelibrary.wiley.com/doi/epdf/10.1111/geb.13203

 -->
